---
title: "APDS R Markdown Example"
author: "Arijit Sen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
identical(knitr::opts_knit$get("rmarkdown.runtime"), "shiny") 
```

## Business Case Description

This dataset consists of Gender, Age, Earning and Points (based on spending) of several consumers for a particular retail institution. Here, by using k-means clustering in unsupervised learning we need to find out the clusters based on Earning and Points for better analysis.

## Project Phases

-   Data Exploration Phase
    -   Describe various tasks done - factor, feature scaling, plots etc.
-   ML Algorithms
    -   Which Algorithm? Why? Comparing model outputs (e.g. annova test)
-   Optimisation
    -   Any optimisation technique used and how it improves the model performance.

## R Code for Exploration..

```{r, echo = FALSE, fig.align='center', fig.cap="Plotting Consumer Income and Score"}
consumer = read.csv('Consumer.csv')
consumer = consumer[4:5]
plot(consumer, xlab='Earning (Annual)', ylab='Points')
```

## No. of Clusters by Elbow Method

```{r, echo = FALSE}

set.seed(10)
wss = vector() #Within Cluster sum of squares
for (i in 1:10) wss[i] = sum(kmeans(consumer, i)$withinss)
plot(1:10,
     wss,
     type = 'b',
     main = paste('The Elbow Method'),
     xlab = 'Number of clusters',
     ylab = 'WCSS Method')

```

## Another Way to have Elbow

```{r, echo = FALSE}
nk = 2:10
set.seed(10)
wcss = sapply(nk, function(k){kmeans(consumer,centers = k)$tot.withinss})
plot (nk,wcss,type="l",xlab="number of k",ylab="WCSS")
```

## Another Way to have Elbow Silhouette

```{r, echo = FALSE}
library(fpc)
sw = sapply(nk,function(k){cluster.stats(dist(consumer), kmeans(consumer,centers=k)$cluster)$avg.silwidth})
plot (nk,sw,type="l",xlab="number of clusters",ylab="Avg. Silhouette width")
```

## Visualize Silhouette in factoextra package

```{r, message = FALSE, echo = FALSE}
library(factoextra)
set.seed(123)
fviz_nbclust(consumer, kmeans, method = "silhouette")
```

## Plotting the Clusters by clustplot

```{r, echo = FALSE}
set.seed(25)
kmeans_consumer = kmeans(x = consumer, centers = 5)
kmeans_cluster = kmeans_consumer$cluster

library(cluster)
clusplot(consumer,
         kmeans_cluster,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of Consumers'),
         xlab = 'Earning',
         ylab = 'Points')

```

## Visualize by factoextra package

```{r, message = FALSE, echo = FALSE}
library(factoextra)
set.seed(123)
fviz_cluster(kmeans_consumer, data = consumer)
```

## Embedding a Shiny App

```{r, echo = FALSE}
library(shiny)
shinyApp(
 ui = fluidPage(
  titlePanel("Predict Horsepower from MPG"),
  sidebarLayout(
    sidebarPanel(
      sliderInput("sliderMPG", "What is the MPG of the car?", 10, 35, value = 20),
      checkboxInput("showModel", "Show/Hide Model ", value = TRUE)
      # submitButton("Submit") ## Delayed Reactivity
      
    ),
    mainPanel(
      plotOutput("plotCars"),
      h3("Predicted Horsepower from Model:"),
      textOutput("pred")
      )
    )
  ),
 
 server = function(input, output) {
  modelCars <- lm(hp ~ mpg, data = mtcars)

  modelCarsPred <- reactive({
    mpgInput <- input$sliderMPG
    predict(modelCars, newdata = data.frame(mpg = mpgInput))
  })
  
  output$plotCars <- renderPlot({
    mpgInput <- input$sliderMPG
    
    plot(mtcars$mpg, mtcars$hp, xlab = "Miles Per Gallon", ylab = "Horsepower", bty = "n", pch = 16,
         xlim = c(10, 35), ylim = c(50, 350))
    
    if(input$showModel){
      abline(modelCars, col = "red", lwd = 2)
    }
    
    legend(25, 250, c("Model Prediction"), pch = 16, col = c("red"), bty = "n", cex = 1.2)
    points(mpgInput, modelCarsPred(), col = "red", pch = 16, cex = 2)
  })    

  output$pred <- renderText({
      modelCarsPred()
    })
}
)
```
